% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=0.6in, right=0.6in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Amir Arsalan Yavari}
\hfill{\it\footnotesize Updated \today}}

% --- Contact information and other items ---

\vspace{0.5cm} 
\begin{center}
\begin{tabular}{lll}
% Line 1: Email, GitHub, office location
\textbf{Email}: \href{mailto:aa.yavari@ce.sharif.edu}{aa.yavari@ce.sharif.edu}     &
\hspace{0.4in} \textbf{GitHub}: \href{https://gitranks.com/profile/arsalanyavari}{github.com/arsalanyavari}  \\

% Line 2: Phone number, LinkedIn, citizenship
\textbf{Website}: \href{https://arsalanyavari.github.io}{AmirArsalanYavari.github.io}  & 
\hspace{0.4in} \textbf{LinkedIn}: \href{https://www.linkedin.com/in/amir-arsalan-yavari}{linkedin.com/in/amir-arsalan-yavari}

\end{tabular}
\end{center}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{8pt}

% Set the width of each column
\begin{longtable}{p{1.7in}p{5.1in}}

% --- Section: Research interests ---

\nohyphens{\textcolor{MidnightBlue}{\textbf{\fontsize{12.6pt}{15pt}\selectfont Interests}}}
& Cloud and Fog Computing, Computer Networking, DevOps \\
& \\

% --- Section: Education ---

\textcolor{MidnightBlue}{\textbf{\fontsize{12.6pt}{15pt}\selectfont Education}} 
& \textbf{Sharif University of Technology (SUT)} \hfill Tehran \\ 
& Master's degree student focusing on Fog Computing. GPA: 3.7/4 \hfill 2023 -- 2025 \\
& Supervisors: Dr. Ali Movaghar and Dr. Shaahin Hessabi  \\
& Thesis title: Computation Offloading and Service Caching in Edge Network \\
& \\

& \textbf{Isfahan University of Technology (IUT)} \hfill Isfahan \\ 
& Bachelor's degree in Secure Computing. GPA: 3.6/4 \hfill 2019 -- 2023 \\
& Project Supervisor: Dr. Elham Mahmoudzadeh \\
& Project title: Automating Software Repair (Fixing Software Semantic Bugs) \\
& \\

% --- Section: Teaching experience ---

{\textcolor{MidnightBlue}{\textbf{\fontsize{12.6pt}{15pt}\selectfont Teaching Experience}}} 
& \textbf{Teaching Assistant at SUT} \hfill Jan 2023 - June \\
& \textbf{Courses:} \textbf{Hardware Testability} and \textbf{Logical Design and Circuits} (Dr. S. Hessabi), \textbf{Computer Networking} (Dr. K. Mizanian) \\
& \\

& \textbf{Teaching Assistant \& Lab Supervisor at IUT} \hfill Sep 2021 - Jul 2024 \\
& \textbf{Lab Supervisor:} \textbf{Computer Networks} (Winter 2023 \& 2024) and \textbf{Operating Systems} (Fall 2022) \\
& \textbf{Teaching Assistant:} \textbf{Computer Networking}, \textbf{Operating Systems} and \textbf{Algorithm Design} (Dr. M. Heidarpour), \textbf{Data Structure} and \textbf{Fundamentals of Programming} (Dr. S. Hosseini), \textbf{Operating Systems} and \textbf{Cloud Computing} (Dr. Z. Zali), \textbf{Advanced Programming} and \textbf{Software Testing} (Dr. S. Bagholizadeh) \\
& \\

% --- Section: Industry experience ---

{\textcolor{MidnightBlue}{\textbf{\fontsize{12.6pt}{15pt}\selectfont Industry Experience}}} 
& {\textbf{Ergo Platform}} \href{https://github.com/rosen-bridge/}{Rosen Bridge} \& \href{https://github.com/ergoraffle/}{Ergo Raffle} Projects \hfill \\
& \textbf{DevOps Engineer and System Administrator} \\
& \hspace{0.15in} $\bullet$ \textbf{Infrastructure \& Configuration:} Managed Proxmox servers, provisioned Proxmox VMs using Terraform, and automated server configurations with Ansible. \\
& \hspace{0.15in} $\bullet$ \textbf{CI/CD:} Built pipelines using GitLab CI/GitHub Actions, developed reusable components/actions, and automated Docker builds, NPM versioning, and Pull Request reviews. \\
& \hspace{0.15in} $\bullet$ \textbf{Security \& Administration:} Hardened servers, mitigated system vulnerabilities, and administered the organization's GitLab instance and runners. \\
& \hspace{0.15in} $\bullet$ \textbf{Operations \& Monitoring:} Dockerized and deployed services, implemented comprehensive monitoring stacks (including Grafana, Prometheus server and agent, Loki, Node Exporter, cAdvisor, Sentry), and configured systemd for automated backups and log rotation. \\
& \\

% --- Section: Various skills (programming, software, languages, etc.) ---

{\textcolor{MidnightBlue}{\textbf{\fontsize{12.6pt}{15pt}\selectfont Skills}}} 
& \textbf{DevOps} Docker, Kubernetes, Proxmox, LXC/LXD, Ansible, Terraform, GitLab, GitHub Actions, Bash/Shell Scripting, Nexus, Changesets, Prometheus (Node, Blackbox, JSON Exporters), Grafana (Loki, Alloy), Telegraf, InfluxDB, Sentry \\
& \textbf{Networking, OS \& Security:} Linux, System Hardening, Nginx, OPNsense \\
& \textbf{Programming:} Python, C/C++, OOP, QT Framework\\
& \textbf{Research \& Academic:} Fog/Cloud/Edge Computing, Distributed/Fault-Tolerant Systems, Storage Systems, Steganography \\
& \textbf{Languages:} Persian (Native), English \\
& \\

% --- Section: Volunteer Activities ---

\textcolor{MidnightBlue}{\textbf{\fontsize{12.6pt}{15pt}\selectfont Volunteer Activities}}
& \textbf{Chairperson, IUT CESSA} \hfill Oct 2021 - Dec 2022 \\
& I was the head of the Computer Engineering Student Scientific Association in Isfahan University of Technology. \\
& \\

& \textbf{Technical Team Leader, IUT-CPC Event} \hfill Oct 2021 - Nov 2021 \\
& I was the Frontend, Backend and DevOps teams leader in Isfahan University of Technology Collegiate Programming Contest 2021. \\
& \\

& \textbf{Central Council Member, APACHEE Club} \hfill Feb 2021 - Oct 2021 \\
& As a member of the APACHEE Club at Isfahan University of Technology, I organized a Steganography conference for students. \\
& \\

% --- End of CV! ---

\end{longtable}
\end{document}
